Deep Reinforcement Learning for Conservation Decisions

### 2021-05-13 manuscript/manuscript.Rmd
Small comments

## Designing and training an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->

Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps. 
Over the course of training, the agent will engage in a trial and error process whereby the agent continually updates weights on a collection of neural networks in response to the environment's reward signal, much like how reinforcement learning is believed to work in living creatures [@cite].
Fundamental to this trial and error process is a balancing of explorative and exploitative behavior.
The agent will occasionally need to propose exploratory actions that may result in higher rewards than previously seen. 
Yet, the agent will also need to occasionally exploit the best perceived sequence of actions which may require marginal improvement to reach optimality.
As the exploration-exploitation is currently unsolved, there are a range of approaches that RL algorithms employ.

>>>>

## Designing and training an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->
<!-- Ecologist job to build environment; CS job to build agent 
      Ok so talk about this in very general terms
      selecting an agent, why you might want to use different ones
-->
Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps. 
Over the course of training, the agent will engage in a trial and error process whereby the agent continually updates weights on a collection of neural networks in response to the environment's reward signal, much like how reinforcement learning is believed to work in living creatures [@cite].
Fundamental to this trial and error process is a balancing of explorative and exploitative behavior.
The agent will occasionally need to propose exploratory actions that may result in higher rewards than previously seen. 
Yet, the agent will also need to occasionally exploit the best perceived sequence of actions which may require marginal improvement to reach optimality.
As the exploration-exploitation is currently unsolved, there are a range of approaches that RL algorithms employ.
